Handbook streamFind: Backend

### 2023-03-07 README.Rmd
Implementation of pkgdown and fixes to roxygen documentation

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) (this repository) is the back-end framework for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is data processing for environmental and quality studies. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

>>>>

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) is the back-end framework for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is data processing for environmental and quality studies. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

## Documentation

Documentation and usage articles can be found in [https://ricardobachertdacunha.github.io/streamFind/](https://ricardobachertdacunha.github.io/streamFind/).
